Digital History in Finland, 1488-1828

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
author plots

```{r 20151209-HDH-TurkuVSOthers, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}

# Let us focus on years 1400-1828
df <- dfo %>% filter(publication_year > 1400 & publication_year < 1829)

# Add indicator field: Turku or Not Turku
myplace <- "Turku"
df$myplace <- rep(NA, nrow(df))
df$myplace[df$publication_place == myplace] <- myplace
df$myplace[!df$publication_place == myplace & df$country == "Finland"] <- "Finland"
df$myplace[!df$country == "Finland"] <- "Foreign"
df$myplace <- factor(df$myplace, levels = rev(c("Foreign", "Finland", "Turku")))

# Keep entries with known publication place and paper consumption
# Group by year/decade and Turku/Other
dfs <- df %>%
  #filter(publication_year >= 1600) %>%
  filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
  group_by(publication_decade, myplace) %>%
  summarise(titles = n(), paper = sum(paper.consumption.km2))

@@

p <- ggplot(dfs, aes(x = publication_decade, y = titles, fill = myplace, order = -as.numeric(myplace))) +
     geom_bar(position = "stack", stat = "identity") +
     ggtitle("Title count") +
     scale_fill_manual(values = c("blue", "black", "darkgreen")) +
     xlab("Publication decade") + ylab("Title count (n)")
print(p)

#p + guides(fill = guide_legend(order = 1))
```

@@

>>>>

```{r 20151209-HDH-TurkuVSOthers, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
# Let us focus on years 1400-1828
df <- dfo %>% filter(publication_year > 1400 & publication_year < 1829) %>%
      filter(!is.na(country)) %>%
      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)

# Add indicator field: Turku or Not Turku
myplace <- "Turku"

df$myplace <- rep(NA, nrow(df))
df$myplace[df$publication_place == myplace] <- myplace
df$myplace[!df$publication_place == myplace & df$country == "Finland"] <- "Finland"
df$myplace[!df$country == "Finland" & !df$publication_place == myplace] <- "Foreign"
df$myplace <- factor(df$myplace, levels = rev(c("Foreign", "Finland", "Turku")))

# Keep entries with known publication place and paper consumption
# Group by year/decade and Turku/Other
dfs <- df %>% group_by(publication_decade, myplace) %>%
  summarise(titles = n(), paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

p <- ggplot(dfs, aes(x = publication_decade, y = titles, fill = myplace, order = -as.numeric(myplace))) +
     geom_bar(position = "stack", stat = "identity") +
     ggtitle("Title count") +
     scale_fill_manual(values = c("blue", "black", "darkgreen")) +
     xlab("Publication decade") + ylab("Title count (n)")
print(p)
```

@@

```{r 20151209-HDH-topauthor, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=6}
# Top author
topa <- names(rev(sort(table(dfo$author))))[1:2]

dfs <- dfo %>% filter(author %in% topa) %>% group_by(author, publication_decade) %>% summarize(paper = sum(paper.consumption.km2, na.rm = T), titles = n())

p1 <- p2 <- ggplot(dfs, aes(x = publication_decade, y = titles, color = author)) + geom_point() + geom_line(size = 2) + scale_color_manual(values = c("blue", "red")) + ggtitle("Title count") + xlab("Publication decade") + ylab("Title count (n)")
print(p1)

p2 <- ggplot(dfs, aes(x = publication_decade, y = paper, color = author)) + geom_point() + geom_line(size = 2) + scale_color_manual(values = c("blue", "red")) + ggtitle("Paper consumption") + xlab("Publication decade") + ylab("Paper (km2)")
print(p2)
```
